Attempt to calculate LENA accuracy for ling/nonling

### 2020-10-17 202010_jslhr/add-lena-ana.Rmd
second clean up, add-lena-ana.Rmd in 202010_jslhr knits

```{r read-data,eval=F}
read.csv("../Metadata/result_final_lisa.csv")->metadata
metadata[1,]

csvs=dir("../../its_to_csv/",pattern="csv")

#count_present=NULL
all_segments=NULL
# extract info from csv's
for(thisits in levels(metadata$filename)){
  csv=grep(thisits,csvs)
  #count_present=c(count_present,length(csv))
  if(length(csv)==1){
    #read in full csv
    read.csv(paste0("../../its_to_csv/",csvs[csv]))->thisdat

@@

  } else print(paste(thisits,"not found"))
}
write.csv(all_segments,"LENA_type_lab.csv",row.names = F)
```

@@

read.csv("LENA_type_lab.csv")->all_segments

>>>>

```{r read-data,eval=F}
read.csv("../Derived_Data/result_final_lisa.csv")->metadata
metadata[1,]

csvs=dir("../Raw_Data/its_to_csv/",pattern="csv")

#count_present=NULL
all_segments=NULL
# extract info from csv's
for(thisits in levels(metadata$filename)){
  csv=grep(thisits,csvs)
  #count_present=c(count_present,length(csv))
  if(length(csv)==1){
    #read in full csv
    read.csv(paste0("../Raw_Data/its_to_csv/",csvs[csv]))->thisdat

@@

  } else print(paste(thisits,"not found"))
}
write.csv(all_segments,"../Derived_Data/LENA_type_lab.csv",row.names = F)
```

@@

read.csv("../Derived_Data/LENA_type_lab.csv")->all_segments
